G85R vs WT (M + F)

### 2023-07-26 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
update

compare = makeContrasts(TktDfGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRMDfxWTM=DEout
sGRMDfxWTM=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktDfGR.M-TktDfWT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRMDfxWTMDf=DEout
sGRMDfxWTMDf=DEout[DEout$FDR<.05,]

@@

all.cpmgenes = unique(c(row.names(cpmdata3),row.names(cpmdata4)))

all.cpmdata = matrix(NA, ncol = 33, nrow = length(all.cpmgenes))
colnames(all.cpmdata) = c(colnames(cpmdata3),colnames(cpmdata4))
row.names(all.cpmdata) = all.cpmgenes

all.cpmdata[row.names(cpmdata3),colnames(cpmdata3)] = cpmdata3
all.cpmdata[row.names(cpmdata4),colnames(cpmdata4)] = cpmdata4

all.groups = groups[colnames(all.cpmdata),]

all.TKT.EdgeR = all.cpmdata[, 1:14]
colnames(all.TKT.EdgeR) = c('GRF.CxDf', 'GRF.CxOE', 
                            'WTF.CxDf', 'WTF.CxOE', 
                            'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
                            'GRM.CxDf', 'GRM.CxOE', 
                            'WTM.CxDf', 'WTM.CxOE', 
                            'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')

row.names(all.TKT.EdgeR) = row.names(all.cpmdata)

all.TKT.EdgeR[,1] = GR.F.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,2] = GR.F.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,3] = WTF.CxDf = WT.F.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,4] = WTF.CxOE = WT.F.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,5] = GRxWT.FC = GRxWT.F3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,6] = GRxWT.FDf = GRxWT.FDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,7] = GRxWT.FOE = GRxWT.FOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,8] = GRM.CxDf = GR.M.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,9] = GRM.CxOE = GR.M.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,10] = WTM.CxDf = WT.M.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,11] = WTM.CxOE = WT.M.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,12] = GRxWT.MC = GRxWT.M3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,13] = GRxWT.MDf = GRxWT.MDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,14] = GRxWT.MOE = GRxWT.MOE3[row.names(all.cpmdata),'FDR']

##write.csv(all.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
##write.csv(all.groups, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
##write.csv(all.TKT.EdgeR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")

@@

>>>>

compare = makeContrasts(TktDfGR.M-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRMDfxWTM3=DEout
sGRMDfxWTM3=DEout[DEout$FDR<.05,]

compare = makeContrasts(TktDfGR.M-TktDfWT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GRMDfxWTMDf3=DEout
sGRMDfxWTMDf3=DEout[DEout$FDR<.05,]

@@

@@

```{r echo = F, include = F}
###Generating new CPM, FDR and FC tables with males and females processed seperately

combined.cpmdata = matrix(0, ncol = ncol(cpmdata2), nrow = nrow(cpmdata2))
colnames(combined.cpmdata) = colnames(cpmdata2)
row.names(combined.cpmdata) = row.names(cpmdata2)

combined.cpmdata[row.names(cpmdata3), colnames(cpmdata3)] = cpmdata3
combined.cpmdata[row.names(cpmdata4), colnames(cpmdata4)] = cpmdata4

combined.FDR = matrix(0, ncol = 14, nrow = nrow(combined.cpmdata))
row.names(combined.FDR) = row.names(combined.cpmdata)

colnames(combined.FDR) = c('GRF.CxDf', 'GRF.CxOE', 
                           'WTF.CxDf', 'WTF.CxOE', 
                           'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
                           'GRM.CxDf', 'GRM.CxOE', 
                           'WTM.CxDf', 'WTM.CxOE', 
                           'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')

combined.FDR[row.names(GR.F.CxDf3), 1] = GR.F.CxDf3[,'FDR']
combined.FDR[row.names(GR.F.CxOE3), 2] = GR.F.CxOE3[,'FDR']

combined.FDR[row.names(WT.F.CxDf3), 3] = WT.F.CxDf3[,'FDR']
combined.FDR[row.names(WT.F.CxOE3), 4] = WT.F.CxOE3[,'FDR']

combined.FDR[row.names(GRxWT.F3), 5] = GRxWT.F3[,'FDR']
combined.FDR[row.names(GRxWT.FDf3), 6] = GRxWT.FDf3[,'FDR']
combined.FDR[row.names(GRxWT.FOE3), 7] = GRxWT.FOE3[,'FDR']

combined.FDR[row.names(GR.M.CxDf3), 8] = GR.M.CxDf3[,'FDR']
combined.FDR[row.names(GR.M.CxOE3), 9] = GR.M.CxOE3[,'FDR']

combined.FDR[row.names(WT.M.CxDf3), 10] = WT.M.CxDf3[,'FDR']
combined.FDR[row.names(WT.M.CxOE3), 11] = WT.M.CxOE3[,'FDR']

combined.FDR[row.names(GRxWT.M3), 12] = GRxWT.M3[,'FDR']
combined.FDR[row.names(GRxWT.MDf3), 13] = GRxWT.MDf3[,'FDR']
combined.FDR[row.names(GRxWT.MOE3), 14] = GRxWT.MOE3[,'FDR']

combined.FC = matrix(0, ncol = 14, nrow = nrow(combined.cpmdata))
row.names(combined.FC) = row.names(combined.cpmdata)

colnames(combined.FC) = c('GRF.CxDf', 'GRF.CxOE', 
                          'WTF.CxDf', 'WTF.CxOE', 
                          'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
                          'GRM.CxDf', 'GRM.CxOE', 
                          'WTM.CxDf', 'WTM.CxOE', 
                          'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')

combined.FC[row.names(GR.F.CxDf3), 1] = GR.F.CxDf3[,'logFC']
combined.FC[row.names(GR.F.CxOE3), 2] = GR.F.CxOE3[,'logFC']

combined.FC[row.names(WT.F.CxDf3), 3] = WT.F.CxDf3[,'logFC']
combined.FC[row.names(WT.F.CxOE3), 4] = WT.F.CxOE3[,'logFC']

combined.FC[row.names(GRxWT.F3), 5] = GRxWT.F3[,'logFC']
combined.FC[row.names(GRxWT.FDf3), 6] = GRxWT.FDf3[,'logFC']
combined.FC[row.names(GRxWT.FOE3), 7] = GRxWT.FOE3[,'logFC']

combined.FC[row.names(GR.M.CxDf3), 8] = GR.M.CxDf3[,'logFC']
combined.FC[row.names(GR.M.CxOE3), 9] = GR.M.CxOE3[,'logFC']

combined.FC[row.names(WT.M.CxDf3), 10] = WT.M.CxDf3[,'logFC']
combined.FC[row.names(WT.M.CxOE3), 11] = WT.M.CxOE3[,'logFC']

combined.FC[row.names(GRxWT.M3), 12] = GRxWT.M3[,'logFC']
combined.FC[row.names(GRxWT.MDf3), 13] = GRxWT.MDf3[,'logFC']
combined.FC[row.names(GRxWT.MOE3), 14] = GRxWT.MOE3[,'logFC']

##write.csv(combined.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
##write.csv(combined.FDR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv")
##write.csv(combined.FC, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv")

### 2023-07-26 TKT_RNAseq/R Code/G85RvsWT_Analysis.Rmd
update

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv"),row.names = 1)
GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

@@

Enrichment = function(sigs){
  genes = setNames(rep(0, nrow(cpmdata)), GeneIDKey[row.names(cpmdata), "Symbol"])
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=kegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=kegg.names[row.names(KEGG),1]

@@

sigs2 = sigs2[apply(cpmdata[sigs2,groups$Group == "GR.M" | groups$Group == "WT.M"], 1, min) > 5]

##sigs = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRF.CxDf"]<=.05]

>>>>

##load all files from github
git.dir = "https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/"
cpmdata = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT_cpmdata.csv"),row.names = 1)
groups  = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.metadata.csv"),row.names = 1)
TKT.EdgeR = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FDRTable.csv"),row.names = 1)
TKT.EdgeR.FC = read.csv(paste0(git.dir,"TKT_RNAseq/CountTables/TKT.EdgeR.FCTable.csv"),row.names = 1)

GeneIDKey = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/GeneralDataFiles/GeneIDKey.csv", row.names = 1)
kegg = readRDS(gzcon(url(paste0(git.dir,"GeneralDataFiles/kegg.symbol2path.RData"))))
kegg.names = read.csv(paste0(git.dir, "GeneralDataFiles/KEGG.names.csv"), row.names = 1)

@@

##mean.cpm; Mean cpm for each gene in each condition (groups$Group). Used for filtering
mean.cpm = matrix(0, ncol = length(unique(groups$Group)), nrow = nrow(cpmdata))
colnames(mean.cpm) = unique(groups$Group)
row.names(mean.cpm) = row.names(cpmdata)
i=1
while(i<=ncol(mean.cpm)){
  mean.cpm[,i]= apply(cpmdata[,row.names(groups[groups$Group == colnames(mean.cpm)[i],])], 1, mean)
  i=i+1
}

i=1
for(i in 1:ncol(TKT.EdgeR)){
  TKT.EdgeR[TKT.EdgeR[,i] == 0,i] = 2
  i=i+1
}

##GO and KEGG Enrichment function

Enrichment = function(sigs, bg){
  genes = setNames(rep(0, length(bg)), bg)
  genes[sigs] = 1
  pwf=nullp(genes,"dm3","geneSymbol")
  GO.wall=goseq(pwf,"dm3","geneSymbol")
  GO.wall$adjp=p.adjust(GO.wall$over_represented_pvalue,method="BH")
  row.names(GO.wall) = GO.wall$category
  KEGG=goseq(pwf,gene2cat=kegg)
  KEGG$adjp=p.adjust(KEGG$over_represented_pvalue,method="BH")
  row.names(KEGG)=substr(as.character(KEGG[,1]),6,13)
  KEGG$Name=kegg.names[row.names(KEGG),1]

@@

##GR vs WT Females

sigs1 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.FC"] <= .05]
bg1 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.FC"]<= 1]

sigs2 = row.names(TKT.EdgeR)[TKT.EdgeR[,"GRxWT.MC"] <= .05]
bg2 = row.names(TKT.EdgeR)[TKT.EdgeR[, "GRxWT.MC"]<= 1]

sigs = intersect(sigs1, sigs2)
bg = unique(c(bg1, bg2))

sigsKEY = GeneIDKey[sigs,]
sigs = sigsKEY$Symbol
bgKEY = GeneIDKey[bg,]
bg = bgKEY$Symbol

sig.cats = Enrichment(sigs, bg)
